Constraints on Cosmic-Ray Particle Populations, Magnetic Fields, and Dark Matter from VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS

### 2011-09-09 ms.tex
spell-checked and typos fixed

We adopt the electron density profile for the Coma cluster that has been inferred from ROSAT X-ray
observations \citep{article:BrielHenryBohringer:1992} and model the spatial and spectral
distribution of CRs according to the model by \citet{article:PinzkePfrommer:2010} that neglects the
contribution of cluster galaxies. Figure \ref{fig:spectrum} shows the expected spectrum of Coma,
normalized to the total flux within the virial radius (dotted lines) and the angular apertures tested in
this study (solid lines). The gamma-ray flux limit of {\em Fermi} in the energy interval of 1--3 GeV
($<0.4^\circ$) is most constraining. However, since the model flux within the finite energy range of
1--3 GeV is smaller by a factor of 1.5, it falls below the flux upper limits and does not yet
constrain the simulation model.  In our further analysis, we use the most constraining {\em Fermi}
flux limits in the energy interval of 1--3 GeV as well as the gamma-ray flux limits of VERITAS in
the energy range above 220 GeV.

@@

In this work we have adopted the DM density profile by Navarro-Frenk-White \citep[NFW;][]{article:NavarroFrenkWhite:1997},
\begin{equation}
\rho_{\chi}(r)=\rho_{s}\left(\frac{r}{r_{s}}\right)^{-1}\left(1+\frac{r}{r_{s}}\right)^{-2},
\end{equation} 
which parameterizes the distribution of DM by the scale radius $r_{s}$ and the scale density $\rho_{s}$. [how where these calculated?]

@@

\section{Discussion and Conclusions}
VERITAS observed the Coma cluster of galaxies for a total of 18.6 hours of high-quality live time between March and May in 2008. No significant excess of gamma-rays above a threshold of about 220 GeV was detected. Flux upper limits at 99\% confidence level were calculated for the cluster core and three member galaxies. The core was considered both as a point-like and spatialy extended source. The obtained flux upper limits were used to constrain properties of the cluster.

@@

\begin{figure*}
\begin{center}
\scalebox{1.0}{\plotone{f4.eps}}
\end{center}
\caption{Integral flux upper limits (this work, Tables~\ref{table:results} and \ref{table:fermi})
  for different integration radii (shown with different colors), assuming $\alpha=2.1$. These are
  compared to simulated integrated spectra of VHE gamma-ray emission, $E_\gamma
  F_\gamma(>E_\gamma)$, from the Coma cluster (again within different apertures). Note that the {\em
    Fermi} limit for the energy interval of 1--3 GeV within the aperture of 0.4$^\circ$ is most
  constraining. Since the model flux within the finite energy range of 1--3 GeV is smaller by a
  factor of 1.5, it falls below the flux upper limits and does not yet constrain the simulation
  model.}
\label{fig:spectrum}
\end{figure*}

>>>>

We adopt the electron density profile for the Coma cluster that has been inferred from ROSAT X-ray observations \citep{article:BrielHenryBohringer:1992} and model the spatial and spectral distribution of CRs according to the model by \citet{article:PinzkePfrommer:2010} that neglects the contribution of cluster galaxies. Figure \ref{fig:spectrum} shows the expected spectrum of Coma, normalized to the total flux within the virial radius (dotted lines) and the angular apertures tested in this study (solid lines). The gamma-ray flux limit of {\em Fermi} in the energy interval of 1--3 GeV ($<0.4^\circ$) is most constraining. However, since the model flux within the finite energy range of 1--3 GeV is smaller by a factor of 1.5 in comparison to the total flux above 1 GeV, it falls below the flux upper limits which do not yet constrain the simulation model.  In our further analysis, we use the most constraining {\em Fermi} flux limits in the energy interval of 1--3 GeV as well as the gamma-ray flux limits of VERITAS in the energy range above 220 GeV.

@@

In this work we have adopted the DM density profile by Navarro-Frenk-White \citep[NFW;][]{article:NavarroFrenkWhite:1997},
\begin{equation}
\rho_{\chi}(r)=\rho_{s}\left(\frac{r}{r_{s}}\right)^{-1}\left(1+\frac{r}{r_{s}}\right)^{-2},
\end{equation} 
which parametrizes the distribution of DM by the scale radius $r_{s}$ and the scale density $\rho_{s}$. [how where these calculated?]

@@

\section{Discussion and Conclusions}
VERITAS observed the Coma cluster of galaxies for a total of 18.6 hours of high-quality live time between March and May in 2008. No significant excess of gamma-rays above a threshold of about 220 GeV was detected. Flux upper limits at 99\% confidence level were calculated for the cluster core and three member galaxies. The core was considered both as a point-like and spatially extended source. The obtained flux upper limits were used to constrain properties of the cluster.

@@

\begin{figure*}
\begin{center}
\scalebox{1.0}{\plotone{f4.eps}}
\end{center}
\caption{Integral flux upper limits (this work, Tables~\ref{table:results} and \ref{table:fermi}) for different integration radii (shown with different colors), assuming $\alpha=2.1$. These are compared to simulated integrated spectra of VHE gamma-ray emission, $E_\gamma F_\gamma(>E_\gamma)$, from the Coma cluster (again within different apertures). Note that the {\em Fermi} limit for the energy interval of 1--3 GeV within the aperture of 0.4$^\circ$ is most constraining. Since the model flux within the finite energy range of 1--3 GeV is smaller by a factor of 1.5 in comparison to the total flux above 1 GeV, it falls below the flux upper limits which do not yet constrain the simulation model.}
\label{fig:spectrum}
\end{figure*}

is smaller by a factor of 1.5 in comparison to the total flux above 1 GeV, it falls below the flux upper limits which do not yet constrain the simulation model.
